Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-26 paper/paper.tex
adding words for the first program

    ;; Returning the distribution and parameters
    [d a b]))
\end{lstlisting}
This query defines a probability distribution on three
variables, $\texttt{d} \in \{\texttt{normal},\texttt{gamma}\}$
for a distribution type, and $\texttt{a}$ and $\texttt{b}$ for
positive parameters for the type. Samples from this distribution
can be obtained by running the query under one of Anglican's
inference algorithms.

>>>>

    ;; Returning the distribution and parameters
    [d a b]))
\end{lstlisting}
The query builds a model for the input $\data$, a sequence of data points.
It defines a probability distribution on three variables, 
$\texttt{d} \in \{\texttt{normal},\texttt{gamma}\}$
for a distribution type, and $\texttt{a}$ and $\texttt{b}$ for
positive parameters for the type. Concretely,
using the $\texttt{sample}$ statements, the query
first defines so called a prior distribution on these three variables,
and then it adjust this prior distribution based on data points in
$\texttt{data}$ using the \texttt{observe} statement.
Samples from this adapted distribution (also called posterior distribution)
can be obtained by running the query under one of Anglican's
inference algorithms.
